Trends of SDR in Thessaloniki

### 2023-06-08 Article.Rmd
Commit 2023-06-08 15:17

  It consists of two paragraphs.
keywords: 
  - keyword1
  - keyword2
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:    false
numbersections: true

@@

... site location description and aerosols effect...

@@

......

@@

........................

@@

Using the mean daily Global radiation we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \ref{fig:trendALL}) and Cloudy-sky (Fig. \ref{fig:trendCLOUD}) conditions the statistical significance of the trends is acceptable (Tab. \ref{tab:trendtable}).

@@

..............

@@

```{r cumsumALL, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-1.pdf")
```

@@

>>>>

  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:    false
numbersections: true

@@

...

site location description and aerosols effect

...

@@

...

...

@@

........

................

@@

Using the mean daily Global radiation we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \ref{fig:trendALL}) and Cloudy-sky (Fig. \ref{fig:trendCLOUD}) conditions, the statistical significance of the trends is acceptable (Tab. \ref{tab:trendtable}).

@@

.....

.........

@@

... different in aggregation ...

```{r cumsumALL, echo=F, fig.cap="Running cumulative sum."}
knitr::include_graphics("./images/CumulativeDailyCumSum-1.pdf")
```

@@

Our result reaffirm the
